### 2019-05-31 paper_05_milestone_issf/article.tex
Comment out paper 5 template boilerplate

\documentclass[a4paper, 12pt, times]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage[font=footnotesize]{caption}

\oddsidemargin 0mm \topmargin 0mm \textheight 247mm \textwidth 160mm
\voffset 0mm \hoffset 0mm \headheight = 0mm \headsep = 0mm
\pagestyle{fancy}
\pagenumbering{arabic}
\fancyhead{}
\cfoot{\footnotesize ${\rm VIII^{th}}$ Int. Symp. on Stratified Flows, San Diego, USA, Aug. 29 - Sept. 1, 2016}
\rfoot{\footnotesize \thepage}
\renewcommand{\headrulewidth}{0pt}
\setcounter{secnumdepth}{2}

\newfont{\tit}{ptmb at 14pt}      %% Commands to use required fonts.
\newfont{\auth}{ptmr at 12pt}
\newfont{\sect}{ptmb at 12pt}
\newfont{\subsect}{ptmb at 11pt}

\titleformat{\section}{\sect}{\thesection}{1em}{}
\titleformat{\subsection}{\subsect}{\thesubsection}{1em}{}

\newcommand{\acknowledgements}[0]{\vspace{16pt} \noindent {\sect Acknowledgements} \vspace{10pt}\\}
\newcommand{\references}[0]{\vspace{16pt} \noindent {\sect References} \vspace{10pt}\\}
\renewcommand{\abstract}[0]{\noindent {\sect Abstract} \vspace{5pt}\\}

@@

\newcommand{\R}{\mathcal{R}}

\newcommand{\eps}{\varepsilon}
\newcommand{\epsK}{\varepsilon_{\!\scriptscriptstyle K}}
\newcommand{\epsA}{\varepsilon_{\!\scriptscriptstyle A}}

\newcommand{\pathfigures}{/fsnet/project/coriolis/2016/16MILESTONE/figure}
% \newcommand{\pathfigures}{/home/pierre/16MILESTONE/Figures}

\begin{document}
\begin{center}

{\tit First report of the MILESTONE experiment: strongly stratified turbulence
and mixing efficiency in the Coriolis platform}\\ %% Title

\vspace{10pt}

{\auth \underline{Antoine Campagne}$^{1}$, Henrik Alfredsson$^{2}$, R\'emi Chassagne$^{1}$, Diane
Micard$^{3}$, Nicolas Mordant$^{1}$, Antonio Segalini$^{2}$, Joel
Sommeria$^{1}$, Samuel Viboud$^{1}$, Ashwin Vishnu Mohanan$^{2}$,\\ Erik
Lindborg$^{2}$ and Pierre Augier$^{1}$}\\ %%Authors

\vspace{10pt}

%%Addresses & emails
{$^{1}$LEGI, Universit\'{e} Grenoble Alpes, CNRS, France}\\
{$^{2}$Royal Institute of Technology (KTH), Department of Mechanics, Stockholm, Sweden}\\
{$^{3}$LMFA, \'Ecole Centrale de Lyon, France}\\

Antoine.Campagne@univ-grenoble-alpes.fr
\end{center}

\abstract

\noindent Strongly stratified turbulence is a possible interpretation of oceanic and
atmospheric measurements. However, this regime has never been produced in a
laboratory experiment because of the two conditions of very small horizontal
Froude number $F_h$ and large buoyancy Reynolds number $\R$ which require a verily large experimental facility. We
present a new attempt to study strongly stratified turbulence experimentally in
the Coriolis platform. The flow is forced by a slow periodic movement of an
array of six vertical cylinders of 25\ cm diameter with a mesh of 75\ cm.
%
Five cameras are used for 3D-2C scanned horizontal particles image velocimetry
(PIV) and stereo 2D vertical PIV.  Five density-temperature probes are used to
measure vertical and horizontal profiles and signals at fixed positions.
%
The first preliminary results indicate that we manage to produce strongly
stratified turbulence at very small $F_h$ and large $\R$ in a laboratory
experiment.

@@

\references
\def\refname{}
\vspace{-0.9in}
\bibliographystyle{apalike}
\bibliography{references}

\end{document}

>>>>

%
% \documentclass[a4paper, 12pt, times]{article}
% \usepackage{graphicx}
% \usepackage{amsmath}
% \usepackage{amssymb}
% \usepackage{natbib}
% \usepackage{fancyhdr}
% \usepackage{titlesec}
% \usepackage[font=footnotesize]{caption}
%
% \oddsidemargin 0mm \topmargin 0mm \textheight 247mm \textwidth 160mm
% \voffset 0mm \hoffset 0mm \headheight = 0mm \headsep = 0mm
% \pagestyle{fancy}
% \pagenumbering{arabic}
% \fancyhead{}
% \cfoot{\footnotesize ${\rm VIII^{th}}$ Int. Symp. on Stratified Flows, San Diego, USA, Aug. 29 - Sept. 1, 2016}
% \rfoot{\footnotesize \thepage}
% \renewcommand{\headrulewidth}{0pt}
% \setcounter{secnumdepth}{2}
%
% \newfont{\tit}{ptmb at 14pt}      %% Commands to use required fonts.
% \newfont{\auth}{ptmr at 12pt}
% \newfont{\sect}{ptmb at 12pt}
% \newfont{\subsect}{ptmb at 11pt}
%
% \titleformat{\section}{\sect}{\thesection}{1em}{}
% \titleformat{\subsection}{\subsect}{\thesubsection}{1em}{}
%
% \newcommand{\acknowledgements}[0]{\vspace{16pt} \noindent {\sect Acknowledgements} \vspace{10pt}\\}
% \newcommand{\references}[0]{\vspace{16pt} \noindent {\sect References} \vspace{10pt}\\}
% \renewcommand{\abstract}[0]{\noindent {\sect Abstract} \vspace{5pt}\\}

@@

% \newcommand{\R}{\mathcal{R}}
%
% \newcommand{\eps}{\varepsilon}
% \newcommand{\epsK}{\varepsilon_{\!\scriptscriptstyle K}}
% \newcommand{\epsA}{\varepsilon_{\!\scriptscriptstyle A}}
%
% \newcommand{\pathfigures}{/fsnet/project/coriolis/2016/16MILESTONE/figure}
% % \newcommand{\pathfigures}{/home/pierre/16MILESTONE/Figures}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% \begin{document}
% \begin{center}
%
% {\tit First report of the MILESTONE experiment: strongly stratified turbulence
% and mixing efficiency in the Coriolis platform}\\ %% Title
%
% \vspace{10pt}
%
% {\auth \underline{Antoine Campagne}$^{1}$, Henrik Alfredsson$^{2}$, R\'emi Chassagne$^{1}$, Diane
% Micard$^{3}$, Nicolas Mordant$^{1}$, Antonio Segalini$^{2}$, Joel
% Sommeria$^{1}$, Samuel Viboud$^{1}$, Ashwin Vishnu Mohanan$^{2}$,\\ Erik
% Lindborg$^{2}$ and Pierre Augier$^{1}$}\\ %%Authors
%
%
% \vspace{10pt}
%
% %%Addresses & emails
% {$^{1}$LEGI, Universit\'{e} Grenoble Alpes, CNRS, France}\\
% {$^{2}$Royal Institute of Technology (KTH), Department of Mechanics, Stockholm, Sweden}\\
% {$^{3}$LMFA, \'Ecole Centrale de Lyon, France}\\
%
% Antoine.Campagne@univ-grenoble-alpes.fr
% \end{center}
%
% \abstract
%
% \noindent Strongly stratified turbulence is a possible interpretation of oceanic and
% atmospheric measurements. However, this regime has never been produced in a
% laboratory experiment because of the two conditions of very small horizontal
% Froude number $F_h$ and large buoyancy Reynolds number $\R$ which require a verily large experimental facility. We
% present a new attempt to study strongly stratified turbulence experimentally in
% the Coriolis platform. The flow is forced by a slow periodic movement of an
% array of six vertical cylinders of 25\ cm diameter with a mesh of 75\ cm.
% %
% Five cameras are used for 3D-2C scanned horizontal particles image velocimetry
% (PIV) and stereo 2D vertical PIV.  Five density-temperature probes are used to
% measure vertical and horizontal profiles and signals at fixed positions.
% %
% The first preliminary results indicate that we manage to produce strongly
% stratified turbulence at very small $F_h$ and large $\R$ in a laboratory
% experiment.

@@

% \references
% \def\refname{}
% \vspace{-0.9in}
% \bibliographystyle{apalike}
% \bibliography{references}
%
%
% \end{document}
